Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2019-11-12 paper2_JNLS/paper.tex
NM

	Since the inverse temperature, $\theta$, is a key modeling parameter, it would be highly desirable to normalize the system such that the value of $\theta$ does not depend sensitively on the truncation index, as $\Lambda$ grows large. That way, $\theta$ can be interpreted as a real physical parameter that can be linked to the experiments and whose value does not depend sensitively on where one chooses to truncate the system. The one modeling parameter that is left to be set is $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. In what follows, we will determine reasonable constraints on $\lamfac$ that allow $\theta$ to be asymptotically independent of $\Lambda$.

@@

\nick{Include a short description of the numerical method for simulation TKdV: a symplectic integrator.}
Two approaches can be applied to predict the statistics in the
downstream wave disturbance, which can be used to confirm each other in
the numerical results. The equilibrium statistical mechanics
is an easy way to confirm the matching condition and get the equilibrium
distribution in far-field long-time limit. On the other hand, the
direct simulations of the dynamical model can offer estimates about
the transient statistics before the far-field equilibrium state is
reached.

Here we describe the direct numerical method used for the simulation of the TKdV equation.

\subsubsection*{Conservation of energy and Hamiltonian form the symplectic scheme}

>>>>

	Since the inverse temperature, $\theta$, is a key modeling parameter, it would be highly desirable to normalize the system such that the value of $\theta$ does not depend sensitively on the truncation index as $\Lambda$ grows large. That way, $\theta$ can be interpreted as a real physical parameter that can be linked to the experiments and whose value does not depend sensitively on where one chooses to truncate the system. The one modeling parameter that is left to be set is $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. In what follows, we will determine reasonable constraints on $\lamfac$ that allow $\theta$ to be asymptotically independent of $\Lambda$.

@@

%Two approaches can be applied to predict the statistics in the downstream wave disturbance, which can be used to confirm each other in the numerical results. The equilibrium statistical mechanics is an easy way to confirm the matching condition and get the equilibrium distribution in far-field long-time limit.  On the other hand, the direct simulations of the dynamical model can offer estimates about the transient statistics before the far-field equilibrium state is reached.

We now detail the method for direct numerical simulation of the TKdV dynamical system \eqref{TKdV}. In particular, the conservation of energy and Hamiltonian plays a central role in the emergent statistical features of the system. Hence, it is important to conserve these quantities numerically and so we use a so-called symplectic scheme.

%In particular, to properly conserve the energy and Hamiltonian over long-time horizon simulations, it is necessary to use a symplectic integrator

\vsp{5}

%\subsubsection*{Conservation of energy and Hamiltonian form the symplectic scheme}
